Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-08 background.tex
tweak Section 2 based on MM and Gail

\subsection{Dragonfly Network}
\label{sec:network}
The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links. In each group, there could be $a$ routers connected via all-to-all local channels. For each router, there could be $p$ compute nodes attached to it via terminal links. The router has $h$ global channels used as intergroup connections through which it connected to other routers in different groups. Thus, the radix of each router is $k = a+h+p-1$. Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network. The adoption of proper $a$, $h$, $p$ involves many factors such as system scale, building cost and workload characteristics.

@@

The routing policy refers to the strategy adopted to route a message (a stream of packets) from the source router to the destination router. Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}. In this work we study three alternative routing policies considered by the community for dragonfly networks.

\textbf{Minimal:} In this policy, a message takes the minimal (shortest) path from the source router to the destination router. When there are multiple minimal paths between the source and destination, the message will be evenly divided among the paths. Minimal routing can guarantee the minimum hops the message takes from the source to the destination. However, it may result in congestion along the minimal paths.

\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths. For the non-minimal path, an intermediate router in a separate group will be randomly chosen. The message takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths. Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.

\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to route a packet (non-)minimally is re-evaluated for each packet generated in the source group, as opposed to once for the entire message; the re-evaulation does not occur in intermediate groups~\cite{jiang}.
Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.

@@

\textbf{Random Placement:} In this policy, an application gets the required number of nodes randomly selected from all the available nodes in the system. As illustrated in Figure~\ref{fig:dragonfly-overview}, $J1$ gets random allocation in which nodes are attached to different routers in different groups. Routers may be shared by different applications and more routers are involved in serving each application when random placement is in use. Random placement can distribute the tasks of an application uniformly across the network to avoid the possible local congestion. However, random placement may cause congestion on global links.

>>>>

\subsection{Dragonfly Network}
\label{sec:network}
The dragonfly is a two-level hierarchical topology, consisting of several groups connected by all-to-all links. In each group, there can be $a$ routers connected via all-to-all local channels. For each router, there can be $p$ compute nodes attached to it via terminal links. The router has $h$ global channels used as intergroup connections through which it connected to other routers in different groups. Thus, the radix of each router is $k = a+h+p-1$. Different computing centers could choose different values for  $a$, $h$, $p$ when deploying their dragonfly network. The adoption of proper $a$, $h$, $p$ involves many factors such as system scale, building cost and workload characteristics.

@@

The routing policy refers to the strategy adopted to route  packets from the source router to the destination router. Previously studied routing policies for dragonfly network include minimal routing, adaptive routing~\cite{dally-dragonfly}, progressive adaptive routing~\cite{jiang} and some of their variations~\cite{won-prog-adaptive}. In this work we study three alternative routing policies considered by the community for dragonfly networks.

\textbf{Minimal:} In this policy, a packet takes the minimal (shortest) path from the source to the destination. The packet first route locally from the source node to the global channel leading to the destination group. It traverses the global channel to the destination group and routes locally to the destination node. 
Minimal routing can guarantee the minimum hops a packet takes from the source to the destination. However, it usually results in congestion along the minimal paths.

\textbf{Adaptive:} In this policy, the path a packet takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths. For the non-minimal path, an intermediate router in a separate group will be randomly chosen. The packet takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths. Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.

\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to route a packet minimally is re-evaluated until a non-minimal route is chosen for the packet or as long as the packet is in its source group; the re-evaulation does not occur in intermediate groups~\cite{jiang}.
Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.

@@

\textbf{Random Placement:} In this policy, an application gets the required number of nodes randomly selected from all the available nodes in the system. As illustrated in Figure~\ref{fig:dragonfly-overview}, $J1$ gets random allocation in which nodes are attached to different routers in different groups. Routers may be shared by different applications and more routers are involved in serving each application when random placement is in use. Random placement can distribute the tasks of an application uniformly across the network to avoid the possible local congestion.
